---
title: "Getting Started with jofou.lib"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with jofou.lib}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  
  # Customize output of figures
  out.width = '80%',
  fig.align = "center",
  fig.width = 7,
  fig.height = 5
)
```

This is how to get started with `jofou.lib`. 

# EDA function:

- Resume et comparaison des variables categotiques: `my_inspect_cat()`
- Coeficient de correlation pour toutes les variables numeriques: `my_inspect_cor()`
- Resume des categories les plus utilisees: `my_inspect_imb()`
- Nombre de valeur manquante pour chaque variable: `my_inspect_na()`
- Resume et comparaison des variables numeriques: `my_inspect_num()` 
- Types de variables disponibles: `my_inspect_types()`
- Distribution des variables numériques: `my_num_dist()`
- Corrélations entre les variables numériques: `my_corr_num_graph()`
- Distribution des variables catégoriques: `my_cat_dist()`

## Load Libraries

Load the following Libraries

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(jofou.lib)
```

## Get the Iris data

The only requirement is that the data must have the type of variables your looking to summarize.

```{r}
head(iris)
```

## Make EDA with the my_inspect group functions

### Step 1: Types of variables

Use `my_inspect_types()` to quickly get a summary of your data. 

```{r}
iris %>%
 my_inspect_types()
```

### Step 2: Look at numeric variables


Use `my_inspect_num()` to quickly get a summary of your numerical variables. 

```{r}
iris %>%
 my_inspect_num()
```

Look at correlation between numerical variables.

```{r}
iris %>%
 my_inspect_cor()
```

Look at the distribution of numeric variables.

```{r}
iris %>%
 my_num_dist()
```

Look at the correlation between numeric variables.

```{r}
iris %>%
 my_corr_num_graph()
```

### Step 4: Look at categorical variables

Use `my_inspect_cat()` to quickly get a summary of your categorical variables.

```{r}
iris %>%
 my_inspect_cat()
```

Or see the most frequently used categorical variables.

```{r}
iris %>%
 my_inspect_imb()
```

Use `my_cat_dist()` to look at the distribution of categorical variables. 

```{r}
iris %>%
 my_cat_dist()
```

### Step 4: Look at NAs

Use `my_inspect_na()` to quickly know where are the NAs in your data.

```{r}
iris %>%
 my_inspect_na()
```


# Utilities function:

- Calculer le mode des variables categotiques: `calculate_mode()`
- Ne contient pas: `%ni%`

## Load Libraries

Load the following Libraries

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(jofou.lib)
```

## Get the Iris data

The only requirement is that the data must have the type of variables your looking to summarize.

```{r}
head(iris)
```

## Function 1: Calculate mode

Use `calculate_mode()` to quickly get the mode of your categorical variable. 

```{r}
iris %>%
  mutate(cat_Sepal.Length=round(Sepal.Length, digits = 0)) %>%
  group_by(cat_Sepal.Length) %>%
  summarise(mode_species=calculate_mode(Species))
```

### Function 2: Not in

Use `%ni%()` remove value in variable.  

```{r}
iris %>%
  filter(Species %ni% "setosa") %>%
  group_by(Species) %>%
  summarise(nb=dplyr::n())
```

# ML function:

- Calibrer et créer un graphique: `calibrate_and_plot()`

## Load Libraries

Load the following Libraries

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)
library(timetk)
library(parsnip)
library(rsample)
library(modeltime)
library(jofou.lib)
```

## Prepare the data

```{r}
data_prepared_tbl <- m4_monthly %>% filter(id == "M750")
# Split Data 80/20
splits <- initial_time_split(data_prepared_tbl, prop = 0.9)
```

## Create a fitted model

```{r}
model_fit_arima <- arima_reg() %>%
   set_engine(engine = "auto_arima") %>%
   fit(value ~ date, data = training(splits))
```

## Function 1: Calibrate and plot

Use `calibrate_and_plot()` to quickly get the visual result of the fitted model. 

```{r}
calibrate_and_plot(model_fit_arima, type="testing")
```
