---
title: "Getting Started with jofou.lib"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with jofou.lib}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  
  # Customize output of figures
  out.width = '100%',
  fig.align = "center",
  fig.width = 7,
  fig.height = 5
)
```

This is how to get started with `jofou.lib`. 

# List functions avalaibles:

- Resume et comparaison des variables categotiques: `my_inspect_cat()`
- Coeficient de correlation pour toutes les variables numeriques: `my_inspect_cor()`
- Resume des categories les plus utilisees: `my_inspect_imb()`
- Nombre de valeur manquante pour chaque variable: `my_inspect_na()`
- Resume et comparaison des variables numeriques: `my_inspect_num()` 
- Types de variables disponibles: `my_inspect_types()`

## Load Libraries

Load the following Libraries

```{r setup, message=FALSE, warning=FALSE}
library(tidyverse)
library(jofou.lib)
```

## Get the Iris data

The only requirement is that the data must have the type of variables your looking to summarize.

```{r}
head(iris)
```



## Make EDA with the my_inspect group functions


### Step 1: Types of variables

Use `my_inspect_types()` to quickly get a summary of your data. 

```{r}
iris %>%
 my_inspect_types()
```

### Step 2: Look at numeric variables


Use `my_inspect_num()` to quickly get a summary of your numerical variables. 

```{r}
iris %>%
 my_inspect_num()
```

Look at correlation between numerical variables.
```{r}
iris %>%
 my_inspect_cor()
```


### Step 4: Look at categorical variables

Use `my_inspect_cat()` to quickly get a summary of your categorical variables.

```{r}
iris %>%
 my_inspect_cat()
```

Or see the most frequently used categorical variables.

```{r}
iris %>%
 my_inspect_imb()
```

### Step 4: Look at NAs

Use `my_inspect_cat()` to quickly know where are the NAs in your data.

```{r}
iris %>%
 my_inspect_na()
```

